SMASH companion source code repository

### 2018-12-04 analysis/index.Rmd
Added shiny page to home.

2. [Plots of the mean and variance functions used to simulate Gaussian data for the mean-estimation experiments.](gaussian_signals.html)

3. [Estimating the variance function from Gaussian-distributed
data.](gaussvarest.html)

>>>>

2. [Plots of the mean and variance functions used to simulate Gaussian data for the mean estimation experiments.](gaussian_signals.html)

3. [Interactive (Shiny) plot for browsing results of Gaussian mean estimation experiments.](gauss_shiny.html)

4. [Estimating the variance function from Gaussian-distributed
data.](gaussvarest.html)
